Cumulant-based Robust Estimates for Network Attack Detection

### 2019-04-20 docs/papers/2019JNCA_m-mcd/2019JNCA_m-mcd.tex
adding initial paper template

\usepackage{lineno,hyperref}
\usepackage[mathletters]{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{algorithm,algorithmic}% http://ctan.org/pkg/algorithms
\usepackage{natbib}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{amsthm,amsmath}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand*\justify{%
	\fontdimen2\font=0.4em% interword space
	\fontdimen3\font=0.2em% interword stretch
	\fontdimen4\font=0.1em% interword shrink
	\fontdimen7\font=0.1em% extra space
	%\hyphenchar\font=`\-% allowing hyphenation
}

@@

\title{Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks}

%% Group authors per affiliation:
\author[unbaddress]{Thiago P. B. Vieira}
\author[unbaddress]{Danilo F. Tenório}
\author[unbaddress,Ilmenauaddress,Fraunhoferaddress]{João Paulo C. L. da Costa}
\author[ufrgsaddress]{\\Edison P. de Freitas}
\author[Ilmenauaddress,Fraunhoferaddress]{Giovanni Del Galdo}
\author[unbaddress]{Rafael T. de Sousa Júnior}

\address[unbaddress]{Department of Electrical Engineering, University of Brasilia (UnB), 70910-900, Brasília-DF, Brazil}
\address[Ilmenauaddress]{Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany}
\address[Fraunhoferaddress]{Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany}
\address[ufrgsaddress]{Graduate Program in Electrical Engineering, Federal University of Rio Grande do Sul (UFRGS), 90035-190, Porto Alegre, Brazil}

\begin{abstract}
Novel schemes for attack detection are crucial to identify adaptive malicious traffic coming from sources that are quickly mobilized by attackers in high throughput communication networks. In this context, signal processing techniques have been applied to attack detection due to their capability to detect anomalies that are previously unknown, i.e. blind detection. This paper proposes a signal processing framework for the detection and identification of network attacks using concepts of model order selection (MOS), eigenvalues and similarity analysis. In order to validate the proposed framework, we consider network traffic datasets that contain malicious activity such as flood and port probing attacks. We propose to model the network traffic as a superposition of components, namely, user's operations (legitimate traffic), network service operation not related to the user (noise) and the malicious activity. The experiments performed in a real network and also using the DARPA 1998 public dataset show that the proposed blind detection approach achieves satisfactory levels of accuracy in terms of timely detection and identification of TCP/UDP ports under attack.
\end{abstract}

\begin{keyword}
Network Attack Detection \sep Model Order Selection \sep Eigen Analysis \sep Similarity Analysis
\end{keyword}

@@

\section{Introduction}
\label{sec:introduction}

@@

In the context of anomaly-based schemes, this work proposes a statistical approach based on signal processing techniques for the detection of malicious traffic in computer networks. Inspired by \cite{david2011blind,da2012improved}, this work models the network traffic using a signal processing formulation as a composition of three components: legitimate traffic, malicious traffic and noise, taking into account the incoming and outgoing traffic in certain types of network ports (TCP or UDP). To the best of our knowledge there is no similar model in the literature. The proposed technique is based on eigenvalue analysis, model order selection (MOS) and similarity analysis. In contrast to \cite{david2011blind,da2012improved,tenorio2013greatest}, MOS and eigenvalue analysis are applied to detect time frames under attack. In addition, we also evaluate the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset \citep{osanaiye2016distributed}, which is a well known network traffic dataset. Furthermore, this proposed approach has its accuracy evaluation based on eigen similarity analysis for extracting detailed information about accurate time and network ports under attack.

The performed experiments show that synflood, fraggle and port scan attacks can be detected accurately and with great detail in an automatic and blind fashion, applying signal processing concepts for traffic modeling and through approaches based on MOS and eigen similarity analysis. The main contributions of the proposed framework are the capability to blindly detect time frames under network attack via MOS and eigen analysis, and the detailed identification of the network attack via eigen similarity analysis.

This paper is organized as follows. In Section \ref{sec:relatedworks}, related works are discussed. Section \ref{sec:datamodel} presents the data model and the evaluated datasets. Section \ref{sec:prop_getv} describes the proposed framework for blind and automatic detection of flood and probe attacks. Section \ref{sec:experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:Complexity} discusses the computational complexity of the proposed framework and evaluates the required processing time for tested scenarios. Section \ref{sec:conclusionandfutureworks} draws the conclusions and the suggestions for future work. The \ref{sec:mos} presents mathematical concepts of examples of state-of-the-art MOS schemes.

\section{Related Works}
\label{sec:relatedworks}

@@

\section{Data Model}
\label{sec:datamodel}

In this paper, scalars are denoted by italic letters (\emph{a, b, A, B, $α$, $β$}), vectors by lowercase bold letters (\textbf{a, b}), matrices by uppercase bold letters (\textbf{A, B}), and $a_i,_j$ denotes the (\emph{i, j}) elements of the matrix \textbf{A}. The superscripts \textsuperscript{T} and \textsuperscript{-1} are used for matrix transposition and matrix inversion, respectively. We define the operator $\rm diag(\cdot)$ that returns the vector of the main diagonal of a given matrix, the operator $\rightarrow$, which denotes the deletion of a given element from a set and the operator $\#$, that returns the rank of a matriz, and the operator $\sim$ that sorts the elements of a vector in ascending order.

This section presents details of the experimental scenario and the selected cases of the DARPA dataset, along with a description of the dataset model as a signal superposition of legitimate traffic, noise and malicious traffic. Subsection \ref{sec:DataCollection} describes the environment and scenario adopted in order to reproduce flood and probe attacks. Subsection \ref{sec:ModelingData} presents how network traffic can be modeled as signal superposition. Subsection \ref{sec:SynfloodFraggleandPortscan} details the traffic of synflood, fraggle and port scan attacks, and Subsection \ref{sec:DarpaDataset} discusses the use of the DARPA dataset for evaluation of the proposed approach.

\subsection{Analyzed Scenario and Data Collection}
\label{sec:DataCollection}

The environment of the analyzed scenario is composed of two computers and one router with access to the Internet and to an internal network, where the simulation of legitimate traffic, noise, flood and port scan attacks are performed. During the traffic generation, one computer assumes the role of the attacker, while the other is the victim, according to scenario represented by Figure \ref{fig:fig1}.

\begin{figure}[h!]
     \centering 
     \includegraphics[height=6cm, width=9cm]{results/figures/fig09.png}
     \caption{Scenario to reproduce legitimate traffic, noise, flood and port scan.}
     \label{fig:fig1}
\end{figure}

Note that the set of network traffic is modeled as legitimate, noise and malicious traffic, where the victim performs legitimate activities, that can be characterized by web access. In many organizations this type of traffic is predominant, since most of corporate services are web-based, such as: web pages, customized web-based systems and cloud services. It is possible to characterize the traffic of a DHCP service as an example of noise associated with the transport layer. For malicious traffic, three types of networks attacks are evaluated: synflood, fraggle and port scan. These attacks are reproduced using well-known security tools, such as Nmap\footnote{http://nmap.org} to port scan, Metasploit\footnote{http://www.metasploit.com} to synflood and Hping\footnote{http://hping.org} to lead the fraggle attack.

A network traffic log is commonly formed by timestamp, protocol, source IP address, source port, destination IP address, destination port and additional information, according to the type of the used transport protocol. The following TCP traffic log is presented in order to exemplify the collected data:
\newline
\newline
\texttt{\justify21:00:34.099289 IP 192.168.1.102.34712 > 200.221.2.45.80: Flags [S], seq 2424058224, win 14600, options [mss 1460, sackOK,TS val 244136 ecr 0,nop,wscale 7], length 0}
\newline

and the following to exemplify UDP traffic log: 
\newline
\newline
\texttt{\justify21:24:42.484858 IP 192.168.1.102.68 > 192.168.1.1.67: BOOTP/DHCP, Request from 00:26:9e:b7:82:be, length 300}
\newline

In the proposed framework, the goal is to detect the anomalies only taking into account the traffic profile, i.e., specific information such as origin IP or day and time of the attack are not considered. Therefore, from the entire log information, we just consider the timestamp (for sequencing), port type and port number.

\subsection{Modeling Data}
\label{sec:ModelingData}

By modeling the dataset as a signal superposition, the network traffic (\textbf{X}) can be characterized as a mixture of three components: legitimate traffic (\textbf{U}), noise (\textbf{N}) and malicious traffic (\textbf{A}), according to the following expression:

\begin{equation}\label{eq:eq01}
\boldsymbol{X}^{(q)} = \boldsymbol{U}^{(q)} + \boldsymbol{N}^{(q)} + \boldsymbol{A}^{(q)},
\end{equation}
where $q$ represents the $q$-th time frame, which is a time grouping of network traffic. The matrix $\boldsymbol{X}^{(q)} \in \mathbb{R}^{M \times N}$ consists of \emph{M} rows and \emph{N} columns. Each row represents a communication port (TCP port or UDP port), and each column represents time bins having a approtiate size, such as one minute. Each element $x_{m,n}^{(q)}$ stands for the number of times that the port $m$ appears at the $n$-th minute, at the $q$-th time frame.

The legitimate traffic $\boldsymbol{U}^{(q)}$ is characterized by the traffic from user's operations. When a user accesses a web page, for example, there is the corresponding TCP/IP traffic to request the page, as well as there is the traffic required to domain name resolution. Figure \ref{fig:fig3} depicts an example of the legitimate traffic obtained during experiments.

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig03.png}
     \caption{Traffic from user's operations, that can be characterized by web access, traffic of well-known applications or network protocols.}
     \label{fig:fig3}
\end{figure}

The traffic that is not associated with user's operations and with malicious traffic is modeled as noise $\boldsymbol{N}^{(q)}$. The automatic acquisition service of logical IP network address (DHCP) is an example of noise. Independently of any user operation, the machine receives an IP address, since it is configured to perform a DHCP address request. Figure \ref{fig:fig4} depicts an example of noise in a network traffic, represented by traffic to ports 67 and 68.

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig04.png}
     \caption{Network traffic of user independent operations for network management.}
     \label{fig:fig4}
\end{figure}

The traffic coming from a malicious activity, such as a synflood or fraggle attack, is represented by the matrix $\boldsymbol{A}^{(q)}$. For this work we only consider the traffic from port scanning and flood attacks.

We define that if the obtained $\#\boldsymbol{A}^{(q)} ≠ 0$, then there is malicious traffic in the evaluated time frame $q$, on the other hand, if the $\#\boldsymbol{A}^{(q)} = 0$, then there is no malicious traffic. This paper shows how to detect the $\#\boldsymbol{A}^{(q)}$, given only the matrix $\boldsymbol{X}^{(q)}$, in order to identify malicious network traffic.

\subsection{Synflood, Fraggle and Port scan}
\label{sec:SynfloodFraggleandPortscan}

The network attacks evaluated by this work are: synflood, fraggle and port scan. The first two attacks can be qualified as flood or denial of service (DoS) attacks, while the last one can be qualified as probe or port scanning attack. DoS attempts to block access to system or network resources and is implemented by either forcing targets to be unavailable through the exploiting of system vulnerabilities, or consuming resources through large amount of network traffic, characterizing flood attacks. Probe attacks scan the networks to collect information about host, such as IP addresses, ports and services.

With respect to the synflood attacks, the attacker sends a large quantity and concurrent successive SYN requests to a target, in order to consume resources and cause a DoS. Figure \ref{fig:fig5} depicts an example of a synflood attack carried out in a real computer network. In an interval of ten minutes, more than 210,000 packets are sent as a synflood attack. This network traffic behavior can be considered an abnormal behavior of network traffic, especially since it is concentrated in a short period of time and presents similar outstanding traffic during the time under attack.

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig05.png}
     \caption{A large quantity of SYN requests to a target, in order to cause a DoS.}
     \label{fig:fig5}
\end{figure}

With respect to the fraggle attack, large packets with UDP echo segments are sent to the broadcast address of a network. Every packet is modified to have the source address of the victim, in order to implement the source address spoofing technique. Therefore, each host receives a huge amount of requests UDP echo and all of them replies to the IP address of the victim, causing a packet flooding aiming a DoS. This attack can affect the entire network, since all hosts receive several requests UDP echo and respond with the ICMP protocol, therefore each host acts as an amplifier of the attack. This last part of the fraggle attack is not taken into account in this work, because the victim receives ICMP (network layer) packets originated from the hosts that are attacked with flooding packet UDP echo. Figure \ref{fig:fig6} depicts an example of the fraggle attack in a real computer network.

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig06.png}
     \caption{Large amount of “UDP echo” requests and replies, causing packet flooding.}
     \label{fig:fig6}
\end{figure}

More than 6,000,000 malicious packets can be counted in an interval of ten minutes, which can be considered an abnormal network traffic, especially due to the concentrated traffic in a short period of time and due to the similarity of the outstanding traffic.

Port scan is the attempt to establish a connection to TCP and UDP ports to identify what services are running or are in the listening state. There are several available port scanning techniques, including: TCP SYN scan, TCP ACK scan and UDP scan. This work evaluates the use of TCP SYN scan and UDP scan.

In TCP SYN scan, a SYN packet is sent to the destination and two types of responses may occur: SYN/ACK or RST/ACK. In the first case, the destination port is in the listening state, in the second case, the destination port is not listening. At the end of each port scanning, a RST/ACK packet is sent by the system that is performing the port scan. Therefore, a full connection or a complete three-way handshake is never established, which makes the detection of the attack sender more difficult, and requires approaches able to identify probe attacks without connection stablishment. The UDP scan technique sends UDP packets to the destination port, and if it responds with a \emph{ICMP port unreachable} message, then it indicates that the scanned port is closed. On the other hand, if a message is not received, then the port is considered as open.

\begin{figure}[h!]
     \centering 
     \includegraphics[height=5cm, width=9cm]{results/figures/fig07.png}
     \caption{Connection attempts in order to identify active ports.}
     \label{fig:fig7}
\end{figure}

Figure \ref{fig:fig7} depicts an example of the port scan attack in a real computer network. Note that the traffic is composed of two packets for each TCP port and one UDP packet to each port. The incoming and outgoing packets analysis, for each port, shows the high correlation and similarity of TCP and UDP traffic during the simulated port scan attack.

\subsection{The DARPA Dataset}
\label{sec:DarpaDataset}

The DARPA 1998 dataset\footnote{https://www.ll.mit.edu/ideval/data/} includes 7 weeks of sniffed traffic saved into raw TCPDUMP packet data, from inside and outside origins, with labeled attacks. The attacks in this dataset
can be grouped into: denial-of-service (DoS); remote to local (R2L), which is characterized by unauthorized access from a
remote machine; user to root (U2R), which is characterized by unauthorized access to local
super-user privileges; and probe attack. Since the proposed approach focus on flood and probe attack, the analysis concentrates on the attacks that present behaviors similar to flood or probe attack. We observe that the most cases of DoS focus on exploit system vulnerabilities instead of on flooding attack. One example is the occurrence of a neptune attack which sends 20 only SYN packets, what is a behavior that differs of the expected flood attack behavior. Therefore, there were selected the cases that simulates several network traffic or numerous connection requests, also known as flooding attack \cite{ahmed2016survey,osanaiye2016distributed}, and the cases that scan ports sending just a few packets. From the simulated probe attacks, we select the cases that rely on TCP or UDP connections.

The data modeling follows the method described by the Subsection \ref{sec:ModelingData}, with time frames of 20 minutes, packet counting aggregation by minute and considering the traffic to the following ports: 20, 21, 22, 23, 25, 79, 80, 88, 107, 109, 110, 113, 115, 143, 161, 389, 443.

\section{Proposed Framework for Detection and Identification of Network Attacks}
\label{sec:prop_getv}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=11cm, width=9cm]{results/figures/mos_eigen_similarity.eps}
     \caption{Overview of The Framework for Detection and Identification of Network Attacks.}
     \label{fig:fig80}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{results/figures/incremental.eps}
     \caption{Traffic selection for incremental approach.}
     \label{fig:fig8}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{results/figures/individualized.eps}
     \caption{Traffic selection for individual approach.}
     \label{fig:fig9}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{results/figures/incremental_individualized.eps}
     \caption{Traffic selection for incremental individualized approach.}
     \label{fig:fig2}
\end{figure}

@@

\section{Experiments and Results}
\label{sec:experimentalresults}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_synflood.eps} 
     \caption{Eigenvalues of the sample covariance matrix (synflood).}
     \label{fig:fig10}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_fraggle.eps}
     \caption{Eigenvalues of the sample covariance matrix (fraggle).}
     \label{fig:fig11}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_portscan.eps}
     \caption{Eigenvalues of the covariance matrix of zero mean and unitary standard deviation (port scan).}
     \label{fig:fig12}
\end{figure}

@@

\section{Performance Evaluation}
\label{sec:Complexity}

This section discusses the computational complexity and the performance evaluation of the proposed framework, focusing on the main steps, which are the eigenvalues decomposition (EVD), largest eigenvalues analysis, application of MOS scheme and eigen similarity analysis, according to Figure \ref{fig:fig80} and equations presented in Section \ref{sec:prop_getv}.

\subsection{Complexity Analysis}
\label{sec:ComplexityAnalysis}
The EVD, calculated according to (\ref{eq:eq06}), requires the previous calculation of covariance matrix, according to Equations (\ref{eq:eq02}), (\ref{eq:eq03}), (\ref{eq:eq04}) and (\ref{eq:eq05}). The covariance matrix calculation is $O(M^2N)$ and the EVD is $O(N^3)$, where $M$ denotes the number of network ports and $N$ denotes the period time. Therefore, the computational complexity for all steps for EVD can be represented as $O(M^2N + N^3)$ and yields an $O(N^3)$ upper bound on the worst-case running time for EVD.

EDC and EFT are the MOS schemes that presented accuracy on the evaluation for the network attack detection. The computational complexity evaluation for MOS focuses on EDC scheme, since EDC requires less processing time than EFT but presents the same accuracy for the evaluated scenario. EDC scheme is $O(Q \log Q + Q + Q \log Q)$ and its worst-case running time can be represented as $O(Q \log Q)$, where $Q$ denotes the number of time frames.

The largest eigenvalue analysis is $O(\hat{d}Q)$, where $\hat{d}$ denotes the number of time frame under attack, according to Algorithm \ref{alg:alg01}. Subsequently, the eigen similarity analysis relies on EVD and cosine similarity analysis, which is $O(N^2)$, for $\hat{d}$ time frames, therefore the eigen similarity analysis is which is $O(\hat{d}(M^2N + N^3 + N^2))$ and yields an $O(N^3)$ upper bound on the worst-case running time for eigen similarity analysis.

Therefore, the proposed framework is $O(N^3 + Q \log Q + \hat{d}Q + N^3)$ and its worst-case running time is $O(N^3)$. The computational complexity of EVD is predominant in the framework, but the approach splits the data into time frames with period time $N$, which makes possible to limitate the growth of $N$ even for evaluations of cases with total time larger than $N$, reducing the impact caused by the computational complexity of EVD.

\subsection{Processing Time Analysis}
\label{sec:ProcessingAnalysis}
For better understanding the scalability and impact of configurations of $N$, $M$ and $Q$, the processing time required for different scenarios of parameter configurations and dataset were evaluated, measuring the processing time of:

\begin{enumerate}
	\item Eigen analysis based on sample covariance of zero mean;
	\item Eigen analysis based on sample covariance of zero mean and unitary standard deviation;
	\item EDC MOS scheme;
\end{enumerate}

The performance evaluation focus on the main steps, which are discussed in subsection \ref{sec:ComplexityAnalysis} regarding the complexity analysis. The data modeling is also a time consuming step, however its processing can be optimized through distributed processing techniques, such as MapReduce, achieving high throughput for packet counting or even for deep packet inspection \cite{Vieira2013}.

The experiments were performed in a desktop computer with a Intel Core i7-4510U 2.00GHz and 16 GB of RAM, considering: variations on the network traffic time; the frame size denoted as $N$; the number of network ports denoted as $M$; the mean processing time for eigen analysis based on sample covariance of zero mean, denoted as 1-time; the mean processing time for eigen analysis based on sample covariance of zero mean and unitary standard deviation, denoted as 2-time; and the mean processing time for EDC MOS scheme, denoted as 3-time. The mean time calculations was obtained from 200 measurement repetitions, in order to obtain reliable values.

\begin{table*}[!t]
	\caption{Processing time of the main steps for anomaly detection}
	\label{tab:11}
	\centering
	\begin{tabular}{|r|r|r|r|r|r|r|}
		\hline \rowcolor{Gray} \begin{tabular}[x]{@{}l@{}}Traffic Time\\(hour)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Frame Size\\(min)\end{tabular}	 & \begin{tabular}[x]{@{}l@{}}Num. Ports\end{tabular}	& \begin{tabular}[x]{@{}l@{}}1-time\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}2-time\\(ms)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}3-time\\(ms)\end{tabular}	\\ \hline
16	& 10	& 17	& 0.7900	& 0.8100	& 0.0650\\ \hline
16	& 20	& 17	& 0.5250	& 0.5950	& 0.0100\\ \hline
16	& 60	& 17	& 0.9700	& 1.1400	& 0.0250\\ \hline
16	& 120	& 17	& 0.6050	& 0.6100	& 0.0050\\ \hline
16	& 60	& 34	& 1.2750	& 1.2200	& 0.0050\\ \hline
16	& 120	& 34	& 1.1200	& 1.1700	& 0.0050\\ \hline
20	& 10	& 17	& 2.7950	& 2.8950	& 1.1000\\ \hline
20	& 20	& 17	& 2.0700	& 2.0200	& 0.3500\\ \hline
20	& 60	& 17	& 1.0250	& 1.0450	& 0.0650\\ \hline
20	& 120	& 17	& 1.0000	& 1.0700	& 0.0350\\ \hline
20	& 60	& 34	& 2.9650	& 3.2100	& 0.0400\\ \hline
20	& 120	& 34	& 2.9950	& 3.1150	& 0.0200\\ \hline
22	& 10	& 17	& 4.7250	& 4.0850	& 1.4600\\ \hline
22	& 20	& 17	& 2.3200	& 2.6800	& 0.2450\\ \hline
22	& 60	& 17	& 1.0700	& 1.1200	& 0.0300\\ \hline
22	& 120	& 17	& 0.9900	& 1.0500	& 0.0250\\ \hline
22	& 60	& 34	& 3.0850	& 3.1250	& 0.0650\\ \hline
22	& 120	& 34	& 2.8100	& 2.9600	& 0.0250\\ \hline
	\end{tabular}
\end{table*}

Table \ref{tab:11} presents the measured results. The experiment considered traffic time of 16, 20 and 22 hours, according to the selected traffic time per day available by the DARPA dataset. Note that the processing time increases according to the increment in traffic time, around 2 or 3 times for 1-time and 2-time, but the worst measured processing time is 4.7250 milliseconds.

According to Table \ref{tab:11}, the processing time increases with the frame size $N$ decreasing, therefore it is possible to evaluate the frame size that produces better identification rates and acceptable processing time. The number of ports evaluated during the proposed scheme is also an important variable regarding processing time optimizations, since the significant increase of processing time observed between scenarios considering 17 or 34 ports, with growth between 7 \% and 199 \%.

\section{Conclusion and Future Works}
\label{sec:conclusionandfutureworks}

>>>>

\usepackage{lineno,hyperref}
\usepackage[mathletters]{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{algorithm,algorithmic}% http://ctan.org/pkg/algorithms
\usepackage{natbib}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{amsthm,amsmath}

% declarations
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand*\justify{%
	\fontdimen2\font=0.4em% interword space
	\fontdimen3\font=0.2em% interword stretch
	\fontdimen4\font=0.1em% interword shrink
	\fontdimen7\font=0.1em% extra space
	%\hyphenchar\font=`\-% allowing hyphenation
}

@@

\title{Cumulant-based Robust Estimates for Network Attack Detection}

%% Group authors per affiliation:
\author[unbaddress]{Thiago P. B. Vieira}
\author[unbaddress,Ilmenauaddress,Fraunhoferaddress]{João Paulo C. L. da Costa}
\author[Ilmenauaddress,Fraunhoferaddress]{Giovanni Del Galdo}

\address[unbaddress]{Department of Electrical Engineering, University of Brasilia (UnB), 70910-900, Brasília-DF, Brazil}
\address[Ilmenauaddress]{Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany}
\address[Fraunhoferaddress]{Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany}

\begin{abstract}
Botnets... In this context, signal processing techniques have been applied to attack detection due to their capability to detect anomalies that are previously unknown, i.e. blind detection, in contaminated or imbalanced data.... This paper proposes a cumulant-based robust estimates for network attack detection, by combining kurtosis and skewess with Minimum Covariance Determinant. In order to validate the proposed framework, we consider CTU-13 dataset. The experiments show that the proposed method achieves satisfactory levels of precisio, recall and F1 score for network attack detection.
\end{abstract}

\begin{keyword}
Network Attack Detection \sep Cumulant \sep Minimum Covariance Determinant \sep Mahalanobis Distance
\end{keyword}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}

@@

Botnets...

In the context of anomaly-based schemes, this work proposes a statistical approach based on cumulants and Mimimum Covariance Determinant (MCD) for network attack detection. To the best of our knowledge there is no similar model in the literature. We evaluate the accuracy of the proposed framework applied to CTU-13 dataset ??, which is a well known network traffic dataset.

The main contributions of the proposed framework are a semi-supervised method for network attack detection, wich does not depend on knowledge of previous attacks and consider only normal network traffic for robust estimates normal traffic...

This paper is organized as follows. In Section \ref{sec:relatedworks}, related works are discussed. Section \ref{sec:datamodel} presents the data model and the evaluated datasets. Section \ref{sec:c_mcd} describes the proposed framework for blind and automatic detection of flood and probe attacks. Section \ref{sec:experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:conclusionandfutureworks} draws the conclusions and the suggestions for future work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Works}
\label{sec:relatedworks}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data Model}
\label{sec:datamodel}

In this paper, scalars are denoted by italic letters (\emph{a, b, A, B, $α$, $β$}), vectors by lowercase bold letters (\textbf{a, b}), matrices by uppercase bold letters (\textbf{A, B}), and $a_i,_j$ denotes the (\emph{i, j}) elements of the matrix \textbf{A}. The superscripts \textsuperscript{T} and \textsuperscript{-1} are used for matrix transposition and matrix inversion, respectively. We define the operator $\rm diag(\cdot)$ that returns the vector of the main diagonal of a given matrix, the operator $\rightarrow$, which denotes the deletion of a given element from a set and the operator $\#$, that returns the rank of a matrix, and the operator $\sim$ that sorts the elements of a vector in ascending order.

This section also presents a description of the data model and data aggregation of the CTU-13 dataset, in Subsection \ref{sec:CTU-13} discusses the use of the CTU-13 dataset for evaluation of the proposed approach.

\subsection{The CTU-13 Dataset}
\label{sec:CTU-13}

...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cumulant-based Minimum Covariance Determinant}
\label{sec:c_mcd}

@@

\begin{figure}[h!]
	\centering
     % \includegraphics[height=11cm, width=9cm]{results/figures/mos_eigen_similarity.eps}
     \caption{Overview of The Framework for Detection and Identification of Network Attacks.}
     \label{fig:fig80}
\end{figure}

@@

\begin{figure}[h!]
     % \includegraphics[height=4cm, width=12.4cm]{results/figures/incremental.eps}
     \caption{Traffic selection for incremental approach.}
     \label{fig:fig8}
\end{figure}

@@

\begin{figure}[h!]
     % \includegraphics[height=4cm, width=12.4cm]{results/figures/individualized.eps}
     \caption{Traffic selection for individual approach.}
     \label{fig:fig9}
\end{figure}

@@

\begin{figure}[h!]
     % \includegraphics[height=4cm, width=12.4cm]{results/figures/incremental_individualized.eps}
     \caption{Traffic selection for incremental individualized approach.}
     \label{fig:fig2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments and Results}
\label{sec:experimentalresults}

@@

\begin{figure}[h!]
	\centering
     % \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_synflood.eps} 
     \caption{Eigenvalues of the sample covariance matrix (synflood).}
     \label{fig:fig10}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     % \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_fraggle.eps}
     \caption{Eigenvalues of the sample covariance matrix (fraggle).}
     \label{fig:fig11}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     % \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_portscan.eps}
     \caption{Eigenvalues of the covariance matrix of zero mean and unitary standard deviation (port scan).}
     \label{fig:fig12}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Works}
\label{sec:conclusionandfutureworks}
